Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
Updates from Overleaf
spider-plot image inserted.
The first paragraph of Results and Discussions.

@@

\begin{figure}[h!]
  \centering
  %\includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider plots of water accessibility variables by typology}
  \label{fig:spider}
\end{figure}
\subsection*{Model results}

>>>>

Across 78 countries in this study, the data provides 28 numerical variables and four descriptive variables. Majority of the data is from 2010 - 2020 (Figure 1). Therefore, we can analyze the global condition of water accessibility by utilizing the most up to date surveys. Most of the variables are related to water accessibility by their locations, time, and water resources. This also allows us to find water accessibility predictor variables and new clustering graphs.

% Across all countries in this study, results show that up to 40% of the national population needs more than 30 minutes to fetch water irrespective of the type of water source used by the household (Table 2). In over half of the countries examined, more than one household out of four lives at over 30 minutes (round-trip) of a water source. About half of the countries show an average collection time higher than 30 minutes. The national average time to collect water is lowest in Madagascar, taking 14 minutes, and reaches 44 minutes in Uganda. Results from dis aggregation by type of source show that the average time to collect improved sources of water is lower or equivalent than for unimproved sources. These findings suggest that the households who must travel further are also often using unimproved sources. Standard deviations show an important variation in collection time within each country, which could demonstrate high inequalities in terms of access to water.
\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}
\subsection*{Model results}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{spider-plot}
  \caption{Spider plots of water accessibility variables by typology}
  \label{fig:spider}
\end{figure}
\subsection*{Model results}
